Finding and controling biases in dark matter halo concentration estimates

### 2016-07-12 paper/ms.tex
minor caption edit

\begin{figure*}
\begin{center}
  \includegraphics[width=0.49\textwidth]{avg_foff_bolshoi.pdf}
  \includegraphics[width=0.48\textwidth]{sigma_foff_bolshoi.pdf}
\end{center}
\vspace{-0.5cm}
\caption{\emph{Left panel}. Average value of the fractional offset ($f_{\rm
    off}$ in Eq. \ref{eq:f_off}) between the concentration in a halo at 
  high resolution versus its downsampled versions. 
  Thick lines
  correspond to massive halos in the Bolshoi simulation, thin lines to
  the Via Lactea simulation.
  For each case close to $10000$ bootstrapping samples are used.
  The velocity method noticeably overestimates the concentration up to
  a factor of $0.20$, 
  while the new method only underestimates the concentrations by up to
  a factor of $0.04$.
  \emph{Right panel.}
  1$\sigma$ uncertainties on the offset and the concentration
  estimates from the integrated mass method.  
  Lines show the width between the 14 and 86 percentiles
  of the $f_{\rm off}$ distribution at fixed particle number. 
  The lines include the results for the three methods: maximum
  velocity, density and integrated mass.
  Grey symbols correspond to the $1\sigma$ uncertainty on each of
  the halos in the Bolshoi Simulation as a result of the MCMC
  sampling. 
  To allow a fair comparison with $f_{\rm off}$, this uncertainty has
  been normalized by the preferred concentration value for each halo. 
  In both cases (bootstrapping for individul halos and MCMC fit of a
  halo population) the $1\sigma$ is of the same order with a
  decreasing behaviour as $1/\sqrt{N_s}$.
  \label{fig:downsampling}}
\end{figure*}

>>>>

\begin{figure*}
\begin{center}
  \includegraphics[width=0.49\textwidth]{avg_foff_bolshoi.pdf}
  \includegraphics[width=0.48\textwidth]{sigma_foff_bolshoi.pdf}
\end{center}
\vspace{-0.5cm}
\caption{\emph{Left panel}. Average value of the fractional offset ($f_{\rm
    off}$ (Eq. \ref{eq:f_off}) between the concentration in a halo at 
  high resolution and its bootstrapped versions. 
  Thick (thin) lines correspond to massive halos in the Bolshoi (Via
  Lactea) simulation.
  For each case close to $10000$ bootstrapping samples are used.
  The velocity method noticeably overestimates the concentration up to
  a factor of $0.20$, 
  while the new method only underestimates the concentrations by up to
  a factor of $0.04$.
  \emph{Right panel.}
  1$\sigma$ uncertainties on the offset and the concentration
  estimates from the integrated mass method.  
  Lines show the width between the 14 and 86 percentiles
  of the $f_{\rm off}$ distribution at fixed particle number. 
  The lines include the results for the three methods: maximum
  velocity, density and integrated mass.
  Grey symbols correspond to the $1\sigma$ uncertainty on each of
  the halos in the Bolshoi Simulation as a result of the MCMC
  sampling. 
  To allow a fair comparison with $f_{\rm off}$, this uncertainty has
  been normalized by the preferred concentration value for each halo. 
  In both cases (bootstrapping for individul halos and MCMC fit of a
  halo population) the $1\sigma$ is of the same order with a
  decreasing behaviour as $1/\sqrt{N_s}$.
  \label{fig:downsampling}}
\end{figure*}
